%%%%%%%%%%%%%%%%%%%%%%%% referenc.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% sample references
% "computer science"
%
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%%%%%%%%%% Springer-Verlag %%%%%%%%%%%%%%%%%%%%%%%%%%

%
% BibTeX users please use
% \bibliographystyle{}
% \bibliography{}
%
% Non-BibTeX users please use
\begin{thebibliography}{99.}
%
% and use \bibitem to create references.
%
% Use the following syntax and markup for your references
%
\bibitem{con0} M. Fischer, M. Pinzger, and H. Gall. Populating a release history database from version 
control and bug tracking systems. Proceedings of the International Conference on Software Maintenance 
(ICSM 03). IEEE Computer Society, 2003.

\bibitem{con1} The Impact of Human Discussions on Just
-In-Time Quality Assurance. Parastou Tourani and Bram Adams. SANER 2016 - 
23rd IEEE International Conference on Software Analysis, Evolution, and Reengineering.

\bibitem{con2}  A. Bernstein, J. Ekanayake, and M. Pinzger. Improving defect prediction 
using temporal features and non linear models. In IWPSE'07, pages 11-18, Dubrovnik, Croatia,
September 2007.

\bibitem{con3} Baysal, O., Kononenko, O., Holmes, R., \& Godfrey, M. W. (2015). Investigating 
technical and non-technical factors influencing modern code review. Empirical Software Engineering, 
1-28.

\bibitem{con4} H. Joshi, C. Zhang, S. Ramaswamy, and C. Bayrak. Local and global recency 
weighting approach to bug prediction. In MSR'07, pages 33-34, Minneapolis, Minnesota, USA,
May 2007. IEEE Computer Society.

\bibitem{con5} M.-T. J. Ostrand, F.-E. J. Weyuker, and R. M. Bell. Predicting the location 
and number of faults in large software systems. IEEE Trans. Softw. Eng., 31(4):340-355, 2005.

\bibitem{con6} J. Sliwerski, T. Zimmermann, and A. Zeller. When do changes induce fixes? In 
MSR'05, pages 24-28, Saint Louis, Missouri, USA, May 2005. ACM.

\bibitem{con7} C. Bird, A. Bachmann, E. Aune, J. Duffy, A. Bernstein, V. Filkov, and P. Devanbu. 
Fair and balanced?: bias in bug-fix  datasets. Proceedings of the the 7th joint meeting of the 
European software engineering conference and the ACM SIGSOFT symposium on The foundations of 
software engineering (FSE 09). Amsterdam, The Netherlands: ACM, 2009, pp. 121–130.

\bibitem{con8} G. Antoniol, K. Ayari, M. Di Penta, F. Khomh, and Y.G. Guhneuc. 
Is it a bug or an enhancement?: a text-based approach to classify change requests. 
Proceedings of the 2008 conference of the center for advanced studies on collaborative research: 
meeting of minds (CASCON 08). Ontario, Canada: ACM, 2008, pp. 304–318.

\bibitem{con9} M. Fischer, M. Pinzger, and H. Gall. Analyzing and relating bug report data for 
feature tracking. In WCRE'03, pages 90-99, Victoria, B.C., Canada, November 2003.

\bibitem{con10} D. Cubranic and G. C. Murphy. Hipikat: Recommending pertinent software development 
artifacts. In ICSE'03, pages 408-418, Washington, DC, USA, 2003.

\bibitem{con11}  A. Schroter, T. Zimmermann, R. Premraj, and A. Zeller. If your bug database could 
talk... In ICSE'06, pages 18-20, Rio de Janeiro, Brazil, September 2006.

\bibitem{con12} T. Zimmermann, R. Premraj, and A. Zeller. Predicting defects for eclipse. In PROMISE'07, 
pages 1-9, Minneapolis, Minnesota, USA, May 2007. IEEE Computer Society.

\bibitem{con13} T. Zimmermann and P. Weissgerber. Preprocessing cvs data for fine-grained analysis. In 
MSR'04, pages 2-6, Edinburgh, Scotland, UK, May 2004. ACM.

\bibitem{con14}  G. A. Liebchen and M. Shepperd. Data sets and data quality in software engineering. In 
PROMISE'08, pages 39-44, New York, NY, USA, 2008.

\bibitem{con15} N. Bettenburg, S. Just, A. Schroeter, C. Weiss, R. Premraj, and T. Zimmermann. Quality of 
bug reports in eclipse. In eTX'07, pages 21-25, Montreal, Canada, October 2007.

\bibitem{con16} N. Bettenburg, S. Just, A. Schroeter, C. Weiss, R. Premraj, and T. Zimmermann. 
What makes a good bug report? Technical report, Saarland University, Saarbrucken, Germany, September 2007.

\bibitem{con17} N. Bettenburg, R. Premraj, T. Zimmermann, and S. Kim. Duplicate bug reports considered 
harmful... really? In ICSM'08, pages 337-345, October 2008.

\bibitem{con18} P. Hooimeijer and W. Weimer. Modeling bug report quality. In ASE'07, pages 34-43, Atlanta, 
Georgia, USA, November 2007.

\bibitem{con19} K. Chen, S. R. Schach, L. Yu, J. Outt, and G. Z. Heller. Open-source change logs. Emp. 
Softw. Eng., 9(3):197-210, 2004.

\bibitem{con20} A. Bachmann and A. Bernstein. Software process data quality and characteristics: a 
historical view on open and closed source projects. In IWPSE-Evol'09, pages 119-128, Amsterdam, The 
Netherlands, August 2009.

\bibitem{con21} J. Aranda and G. Venolia. The secret life of bugs: Going past the errors and omissions 
in software repositories. In ICSE'09, pages 298-308, May 2009.

\end{thebibliography}
